Sparsity Weak Lensing Mass Reconstruction

### 2020-07-27 paper_ms_method_HSCY1/ms.tex
commit

\subsection{The Problem}
\subsubsection{Density Contrast to Shear}
We first review how the foreground density contrast induces the shear distortion on background galaxies.
The lensing distortion $\kappa$ at a position $\vec{x}=(\vec{\theta}$, $\chi_s$) caused by the foreground 
inhomogeneous density distribution is

@@

\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s} \frac{\delta(\chi_l \vec{\theta},\chi_l)}{a(\chi_l)}
\end{equation}
\citep{massMap-Glimpse3D2014}.
Substitute angular distance $D$ with redshift $z$ and we have
\begin{equation}\label{eq-delta2kappa}
\kappa(\vec{\theta},z_s)=\int_0^{z_s} dz_l \delta_{c}^{-1}(z_l,z_s)\delta(\vec{\theta},z_l).
\end{equation}
we term $\delta_{c}(z_l,z_s)$ as lensing critical density contrast and define it as
\begin{equation}
\delta_{c}^{-1}(z_l,z_s) =
\begin{cases}
\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{\chi_{s} E\left(z_l\right)} & (z_s>z_l),\\
0&(z_s \leq z_l).
\end{cases}
\end{equation}

As reported in \citet{massMap-KS1993}, the shear distortion is
\begin{equation}\label{eq-kappa2gamma}
\vecb{\gamma}(\vec{\theta},z_s) = \int \vecb{D}(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s) d^2 \theta,
\end{equation}
where
\begin{equation}
\begin{split}
\vecb{D}(\vec{\theta})&=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2},\\
\vecb{\gamma}(\vec{\theta})&=\gamma_1(\vec{\theta})+i\gamma_2(\vec{\theta}).
\end{split}
\end{equation}

@@

\subsubsection{Photo-$z$ Uncertainty}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
 \caption{The $1$-D slices of NFW atoms with different scale radius ($r_s=0,1,2,4,8$).}
\end{figure}
Since the redshifts of source galaxies are estimated with a limited number of photometric bands, the estimated redshift of a galaxy suffer from large uncertainty. The probability distribution function (PDF) of a galaxies at position $(\vec{\theta},z_s)$ is denoted as $\mathcal{P}(z|z_s)$.  Note that, in order to simplify the future calculation, we assume the variation of the PDF across the transverse plane is small and neglect the dependency on the transverse position.

>>>>

\subsection{The Problem}
\subsubsection{Density Contrast to Shear}
We first review how the foreground density contrast induces the shear distortion on background galaxies.
The lensing distortion $\kappa$ at a comoving distance $\chi_s$ caused by the foreground inhomogeneous 
density distribution at a comoving distance $\chi_l$ ($\chi_l< \chi_s$) is

@@

\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
\end{equation}
\citep{massMap-Glimpse3D2014}.
where $\chi$ refers to the comoving distance, $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed 
of light, and $a(\chi_l)$ is the scale parameter at the lens position.

Substitute comoving distance ($\chi$) with redshift ($z$)
$z$ and we have
\begin{equation}\label{eq-delta2kappa}
\kappa(\vec{\theta},z_s)=\int_0^{z_s} dz_l \delta_{c}^{-1}(z_l,z_s)\delta(\vec{\theta},z_l).
\end{equation}
We term $\delta_{c}(z_l,z_s)$ as lensing critical density contrast and define it as
\begin{equation}
\delta_{c}^{-1}(z_l,z_s) =
\begin{cases}
\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{\chi_{s} E\left(z_l\right)} & (z_s>z_l),\\
0&(z_s \leq z_l).
\end{cases}
\end{equation}

As shown in \citet{massMap-KS1993}, the shear distortion is related to the kappa field at the redshift plane as
\begin{equation}\label{eq-kappa2gamma}
\vecb{\gamma}(\vec{\theta},z_s) = \int \vecb{D}(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s) d^2 \theta,
\end{equation}
where
\begin{equation}
\begin{split}
\vecb{D}(\vec{\theta})&=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2},\\
\vecb{\gamma}(\vec{\theta})&=\gamma_1(\vec{\theta})+i\gamma_2(\vec{\theta}).
\end{split}
\end{equation}

@@

\subsubsection{Photo-$z$ Uncertainty}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
 \caption{The $1$-D slices of NFW atoms with different scale radius ($r_s=0,1,2,4,8$).}
\end{figure}
Since the redshifts of source galaxies in the current large scale survey are estimated with a limited 
number of photometric bands, the estimated redshift of a single galaxy suffers from large uncertainty. 
We denote the probability of a galaxies, with photo-$z$ estimated as $z_s$, being  located at redshift 
$z$ as $\mathcal{P}(z|z_s)$.  Note that, in order to simplify the future calculation, we assume the 
variation of the PDF across the transverse plane is small and neglect such variation.
